Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-07 WSSSPE3/report/wg_main_industry_interaction.tex
notes/changes in Industry Interaction section

\subsubsection{Why it is important}

@@

At WSSSPE 3 our group was interested in better understanding successful pathways for scientific software to ``transition'' from government-funded research projects to industry sponsorship. 
(This may be an initially awkward phrase---some software projects will begin their life being sponsored by industry, or result in collaboration between industry and academia. 
In such cases, there is still a need to understand how IP and how maintenance of the software is sustained over time)

@@

We characterize sustainability in the following ways:
\begin{itemize}
\item Weak Sustainability: Software continues to be accessible, useful, and usable. 
\item Strong Sustainability: Software meets criteria above, but is also able to be reused for further innovation (i.e., issued non-restrictive open-source license).
\end{itemize}
See Becker et al.~\cite{Becker:2014} for extended discussion of weak vs.\ strong sustainability.

@@

\todo{where should someone go who want to know more about this and perhaps wants to contribute?}

>>>>

%\subsubsection{Why it is important}

@@

At WSSSPE3 our group was interested in better understanding successful pathways for scientific software to ``transition'' from government-funded research projects to industry sponsorship. 
(This may be an initially awkward phrase---some software projects will begin their life being sponsored by industry, or result in collaboration between industry and academia. 
In such cases, there is still a need to understand how IP and how maintenance of the software is sustained over time)

@@

We characterize sustainability in the following ways:
\begin{itemize}
\item Weak Sustainability: Software continues to be accessible, useful, and usable. 
\item Strong Sustainability: Software meets criteria above, but is also able to be reused for further innovation (i.e., issued non-restrictive open-source license).
\end{itemize}
See Becker et al.~\cite{Becker:2014} for extended discussion of weak vs.\ strong sustainability.
For more detail on the group's discussion, see Appendix~\ref{sec:appendix_industry_interaction}.

@@

To find more information about this group, or join it, see \todo{where should someone go who want to know more about this and perhaps wants to contribute?}
